---
title: "TidyTemplate"
date: 2021-05-14
output: html_output
editor_options: 
  chunk_output_type: console
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
library(lubridate)
theme_set(theme_light())

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-04-20")

netflix_titles <- tt$netflix_titles %>% 
  separate(duration, c("duration", "duration_units"), 
           sep = " ", convert = TRUE) %>% 
  mutate(date_added = mdy(date_added),
         year_added = year(date_added))
```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt$netflix_titles %>% 
 summarise(min(release_year), max(release_year))
```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}
netflix_titles %>% 
 ggplot(aes(release_year, fill = type)) + 
 geom_histogram(binwidth = 5) +
 facet_wrap(~ type, ncol = 1, scales = "free_y")

netflix_titles %>% 
 count(year = release_year, type) %>% 
 group_by(type) %>% 
 mutate(percent = n/sum(n)) %>% 
 ggplot(aes(year, percent, color = type)) +
 geom_line()
```


Rank by country (mine)
```{r}
netflix_titles %>%
  mutate(country = fct_lump(country, n = 20)) %>%
  count(country, sort = TRUE) %>%
  filter(!is.na(country)) %>%
  mutate(
    country = fct_reorder(country, n),
    percent = 100 * (n / sum(n))
  ) %>%
  ggplot(aes(country, percent)) +
  geom_col(fill = "green") +
  coord_flip()
```


By decade

```{r}
netflix_titles %>% 
  count(decade = 10 * (release_year %/% 10), type) %>% # %/% is trucated division
  group_by(type) %>% 
  mutate(percent = n/sum(n)) %>% 
  ggplot(aes(decade, percent, color = type)) +
  geom_line()
```


```{r}
netflix_titles %>% 
  count(Rating = rating, sort = TRUE)
```

And for duration
```{r}
netflix_titles %>% 
  count(type, duration_units)
```
Duration of movies are in minutes and TV shows are in season(s)


```{r}
netflix_titles %>% 
  filter(type == "Movie") %>% 
  mutate(decade = 10 * (release_year %/% 10)) %>% 
  ggplot(aes(decade, duration, group = decade)) +
  geom_boxplot()
```


```{r}
netflix_titles %>% 
  separate_rows(listed_in, sep = ", ") %>% 
  count(listed_in, sort = TRUE)
```


```{r}
netflix_titles %>% 
  separate_rows(listed_in, sep = ", ") %>% 
  group_by(type, genre = listed_in) %>% 
  summarise(n = n(), median_duration = median(duration)) %>% 
  arrange(desc(n)) %>% 
  filter(type == "Movie") %>%
  filter(genre != "Movies") %>% 
  mutate(genre = fct_reorder(genre, median_duration)) %>% 
  ggplot(aes(median_duration, genre)) +
  geom_col()
```

Write a function
```{r}
summarize_titles <- function(tbl) {
  tbl %>%
    summarise(
      n = n(),
      median_duration = median(duration),
      median_year = median(release_year)
    ) %>%
    arrange(desc(n))
}
```


```{r}
netflix_titles %>% 
  separate_rows(listed_in, sep = ", ") %>% 
  group_by(type, genre = listed_in) %>% 
  summarize_titles()
```


```{r}
netflix_titles %>% 
  separate_rows(listed_in, sep = ", ") %>% 
  group_by(type, genre = listed_in) %>% 
  summarize_titles() %>% 
  filter(type == "Movie") %>%
  filter(genre != "Movies") %>% 
  mutate(genre = fct_reorder(genre, median_duration)) %>% 
  ggplot(aes(median_duration, genre)) +
  geom_col()
```


Date Added

```{r}
head(netflix_titles$date_added)
```


```{r}
netflix_titles %>% 
  filter(!is.na(date_added)) %>% 
  count(year_added = year(date_added))
```


```{r}
netflix_titles %>% 
  filter(!is.na(date_added)) %>% 
  arrange(date_added) %>% 
  select(type, title, date_added)

netflix_titles %>% 
  filter(!is.na(date_added)) %>% 
  mutate(year_added = pmax(year_added, 2015)) %>% 
  count(year_added, type) %>% 
  ggplot(aes(year_added, n, fill = type)) +
  geom_area()

netflix_titles %>% 
  mutate(year_added = pmax(year_added, 2015)) %>% 
  filter(!is.na(date_added), !is.na(rating)) %>% 
  count(year_added, rating = fct_lump(rating, 6)) %>% 
  ggplot(aes(year_added, n, fill = rating)) +
  geom_area()

# The same as above but using percents
netflix_titles %>% 
  mutate(year_added = pmax(year_added, 2015)) %>% 
  filter(!is.na(date_added), !is.na(rating)) %>% 
  count(year_added, rating = fct_lump(rating, 6)) %>% 
  group_by(year_added) %>% 
  mutate(percent = n/sum(n)) %>% 
  ggplot(aes(year_added, percent, fill = rating)) +
  geom_area()

# Do the same as above by type
netflix_titles %>% 
  filter(!is.na(date_added), !is.na(rating), year_added >= 2015) %>% 
  group_by(type) %>% 
  mutate(rating = fct_lump(rating, 4)) %>% 
  ungroup() %>% 
  count(type, year_added, rating) %>% 
  group_by(type, year_added) %>% 
  mutate(percent = n/sum(n)) %>% 
  ggplot(aes(year_added, percent, fill = rating)) +
  geom_area() +
  facet_wrap(~ type)
```


Let's focus on country

```{r}
netflix_titles %>% 
  filter(!is.na(country)) %>% 
  count(country = fct_lump(country, 20), type, sort = TRUE) %>% 
  mutate(country = fct_reorder(country, n)) %>% 
  ggplot(aes(n, country, fill = type)) +
  geom_col()

netflix_titles %>% 
  filter(!is.na(country), type == "Movie") %>% 
  group_by(country) %>% 
  summarize_titles()
```

Let's see which country make the most R rated movies/TV shows
```{r}
netflix_titles %>% 
  filter(rating == "R") %>% 
  count(country, sort = TRUE)

netflix_titles %>% 
  filter(rating %in% c("R", "TV-MA")) %>% 
  count(country, sort = TRUE)

netflix_titles %>%
  filter(!is.na(rating), !is.na(country)) %>%
  group_by(type, country = fct_lump(country, 9)) %>%
  summarise(
    pct_r_ma = mean(rating %in% c("R", "TV-MA")),
    n = n(),
    .groups = "drop"
  ) %>%
  arrange(desc(n))


netflix_titles %>%
  filter(!is.na(rating), !is.na(country)) %>%
  group_by(type, country = fct_lump(country, 9)) %>%
  summarise(
    n_mature = sum(rating %in% c("R", "TV-MA", "NC-17")),
    n = n(),
    .groups = "drop"
  ) %>%
  mutate(
    pct_mature = n_mature / n,
    conf_low = qbeta(.025, n_mature + .5, n - n_mature + .5),
    conf_high = qbeta(.975, n_mature + .5, n - n_mature + .5)
  ) %>% 
  ggplot(aes(pct_mature, country, color = type)) + 
  geom_point(aes(size = n)) + 
  geom_errorbar(aes(xmin = conf_low, xmax = conf_high), width = .1 ) +
  scale_x_continuous(labels = percent) + 
  expand_limits(x = 0) + 
  labs(x = "% of titles that are R/TV-MA")
```


Now to prediction and text mining
```{r}
library(tidytext)
library(snakecase)
library(tidylo)

words_unnested <- netflix_titles %>% 
  unnest_tokens(word, description) %>% 
  anti_join(stop_words, by = "word") 

words_unnested %>% 
  count(type, word, sort = TRUE) %>% 
  mutate(type = to_snake_case(type)) %>% 
  spread(type, n, fill = 0) %>% 
  mutate(total = movie + tv_show) %>% 
  arrange(desc(total)) %>% 
  head(100) %>% 
  ggplot(aes(movie, tv_show)) +
  geom_point() +
  geom_text(aes(label = word), vjust = 1, hjust = 1) +
  scale_x_log10() + 
  scale_y_log10()

words_unnested %>% 
  count(type, word) %>% 
  bind_log_odds(type, word, n) %>% 
  arrange(desc(log_odds_weighted)) %>% 
  group_by(type) %>% 
  top_n(10, log_odds_weighted) %>% 
  ungroup() %>% 
  mutate(word = fct_reorder(word, log_odds_weighted)) %>% 
  ggplot(aes(log_odds_weighted, word)) +
  geom_col() +
  facet_wrap(~ type, scales = "free_y")

```


```{r}
library(widyr)
library(ggraph)

words_unnested %>% 
  distinct(type, title, word) %>% 
  add_count(word, name = "word_total", sort = TRUE) %>% 
  filter(word_total >= 20) %>% 
  pairwise_cor(word, title, sort = TRUE)

# Find out which words appear with crime a lot
words_unnested %>% 
  distinct(type, title, word) %>% 
  add_count(word, name = "word_total", sort = TRUE) %>% 
  filter(word_total >= 20) %>% 
  pairwise_cor(word, title, sort = TRUE) %>% 
  filter(item1 == "crime")

set.seed(2021)
words_unnested %>%
  distinct(type, title, word) %>%
  add_count(word, name = "word_total") %>%
  filter(word_total >= 40) %>%
  pairwise_cor(word, title, sort = TRUE) %>%
  filter(correlation >= .1) %>%
  igraph::graph_from_data_frame() %>%
  ggraph(layout = "fr") +
  geom_edge_link(aes(alpha = correlation)) +
  geom_node_point() +
  geom_node_text(aes(label = name),
    repel = TRUE
  ) +
  theme(legend.position = "none")
```


```{r}
word_genre_log_odds <- words_unnested %>% 
  distinct(type, title, word, genre = listed_in) %>% 
  separate_rows(genre, sep = ", ") %>% 
  filter(fct_lump(genre, 9) != "Other") %>% 
  count(genre, word) %>% 
  bind_log_odds(genre, word, n)
```


```{r}
word_genre_log_odds %>%
  group_by(genre) %>%
  top_n(10, log_odds_weighted) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, log_odds_weighted, genre)) %>%
  ggplot(aes(log_odds_weighted, word, fill = genre)) +
  geom_col() +
  facet_wrap(~ genre, scales = "free_y") +
  scale_y_reordered() +
  theme(legend.position = "none") +
  labs(x = "Log-odds of word's specificity to genre",
       y = "")
```


## Lasso Regression

```{r}
word_ratings <- words_unnested %>% 
  count(type, title, rating, word) %>% 
  filter(!is.na(rating)) %>% 
  mutate(mature = rating %in% c("TV-MA", "R", "NC-17")) %>% 
  add_count(word, name = "word_total") %>% 
  filter(word_total >= 30)
```


```{r}
library(glmnet)
library(broom)

other_features <- netflix_titles %>%
  select(title, director, cast, genre = listed_in, country) %>%
  gather(feature_type, feature, director, cast, genre, country) %>%
  filter(!is.na(feature)) %>%
  separate_rows(feature, sep = ", ") %>%
  mutate(feature_type = str_to_title(feature_type)) %>%
  unite(feature, feature_type, feature, sep = ": ") %>%
  add_count(feature, name = "feature_count") %>%
  filter(feature_count >= 10)

feature_matrix <- word_ratings %>%
  mutate(feature = paste("Description:", word)) %>%
  bind_rows(other_features) %>%
  cast_sparse(title, feature)

y <- netflix_titles$mature[match(rownames(feature_matrix), netflix_titles$title)]

mod <- cv.glmnet(feature_matrix, y, family = "binomial")

plot(mod)

mod$glmnet.fit %>%
  tidy() %>%
  separate(term, c("feature_type", "feature"), sep = ": ") %>%
  filter(lambda == mod$lambda.1se) %>%
  top_n(60, abs(estimate)) %>%
  mutate(feature = fct_reorder(feature, estimate)) %>%
  ggplot(aes(estimate, feature, fill = feature_type)) +
  geom_col() +
  labs(
    x = "Coefficient: does this make the title more likely to be TV-MA/R?",
    y = "",
    fill = "Feature Type"
  )
```












