---
title: "Analyzing Deforestation in R"
date: 2022-09-03
output: html_document
editor_options: 
  chunk_output_type: console
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
library(tidytext)
library(fuzzyjoin)
library(ggthemes)
theme_set(theme_light())

```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-04-06")

```


```{r}

tt$forest %>% 
  count(entity, sort = TRUE) %>% 
  count(n)

tt$forest_area %>% 
  count(year)

forest_area <- tt$forest_area

```

```{r}

forest_area %>% 
  filter(entity == "United States") %>% 
  ggplot(aes(year, forest_area)) +
  geom_line() +
  expand_limits(y = 0)

forest_area %>% 
  group_by(year) %>% 
  summarize(sum(forest_area)) %>% 
  View()

forest_area %>% 
  filter(year == max(year)) %>% 
  arrange(desc(forest_area))

forest_area_country <- forest_area %>% 
  filter(str_length(code) == 3, year >= 1992) %>% 
  rename(country = entity) %>% 
  mutate(forest_area = forest_area / 100)

forest_area_country %>% 
  filter(year == max(year)) %>% 
  arrange(desc(forest_area)) 

forest_area_country %>% 
  group_by(year) %>% 
  summarize(sum(forest_area)) 

forest <- tt$forest %>% 
  filter(str_length(code) == 3) %>% 
  rename(country = entity)
  
  
```


```{r}

# line plot for a selected number of countries
forest_area_country %>% 
  filter(country %in% c("United States", "Canada", "China", "India", "Brazil", "Russia")) %>% 
  mutate(country = fct_reorder(country, -forest_area)) %>% 
  ggplot(aes(year, forest_area, color = country)) +
  geom_line() +
  scale_y_continuous(labels = percent) +
  expand_limits(y = 0) +
  labs(
    x = "Year", y = "% of global forest area", color = "Country"
  )

# area plot
forest_area_country %>% 
  mutate(country = fct_lump(country, 9, w = forest_area)) %>% 
  group_by(country, year) %>% 
  summarize(forest_area = sum(forest_area), .groups = "drop") %>% 
  mutate(country = fct_reorder(country, -forest_area)) %>%
  ggplot(aes(year, forest_area, fill = country)) +
  geom_area() +
  scale_y_continuous(labels = percent) +
  expand_limits(y = 0) +
  labs(
    x = "Year", y = "% of global forest area", fill = "Country"
  )

forest_area_country %>% 
  filter(year %in% c(1992, 2020)) %>% 
  mutate(year = paste0("forest_area", year)) %>% 
  spread(year, forest_area) %>% 
  arrange(desc(forest_area1992))

```

```{r}

forest %>% 
  group_by(year) %>% 
  summarize(net_forest_conversion = sum(net_forest_conversion))

forest %>% 
  filter(year == 2015) %>% 
  arrange(net_forest_conversion) %>% 
  slice_max(abs(net_forest_conversion), n = 20) %>% 
  mutate(country = fct_reorder(country, net_forest_conversion)) %>% 
  ggplot(aes(net_forest_conversion, country, fill = (net_forest_conversion > 0) )) +
  geom_col() +
  scale_x_continuous(labels = comma) +
  theme(legend.position = "none") +
  labs(x = "Net change in forest in 2015 (hectares)", y = "")

forest %>% 
  group_by(year) %>% 
  slice_max(abs(net_forest_conversion), n = 10) %>% 
  ungroup() %>% 
  mutate(country = reorder_within(country, net_forest_conversion, year)) %>% 
  ggplot(aes(net_forest_conversion, country, fill = (net_forest_conversion > 0) )) +
  geom_col() +
  facet_wrap(~ year, scales = "free_y") +
  scale_x_continuous(labels = comma) +
  scale_y_reordered() +
  theme(legend.position = "none"kjldfjsldfjsldf) +
  labs(x = "Net change in forest in 2015 (hectares)", y = "")

forest %>% 
  mutate(country = fct_lump(country, 8, w = abs(net_forest_conversion))) %>% 
  group_by(country, year) %>% 
  summarize(net_forest_conversion = sum(net_forest_conversion), .groups = "drop") %>% 
  mutate(country = fct_reorder(country, -net_forest_conversion)) %>% 
  ggplot(aes(year, net_forest_conversion, color = country)) +
  geom_line() +
  scale_y_continuous(labels = comma) +
  labs(x = "Year", y = "Net change in forest area (hectares)", color = "Country")
  

```

```{r}

brazil_loss <- tt$brazil_loss %>% 
  pivot_longer(
    commercial_crops:small_scale_clearing,
    names_to = "causes",
    values_to = "loss"
  ) %>% 
  mutate(causes = str_to_sentence(str_replace_all(causes, "_", " ")))

brazil_loss %>% 
  filter(year == max(year)) %>% 
  arrange(desc(loss)) %>% 
  mutate(causes = fct_reorder(causes, loss)) %>% 
  ggplot(aes(loss, causes)) +
  geom_col() +
  scale_x_continuous(labels = comma) +
  labs(title = "Causes of loss of forest in Brazil in 2013",
       x = "Loss (hectares)", y = "")

brazil_loss %>% 
  mutate(causes = fct_reorder(causes, -loss)) %>% 
  ggplot(aes(year, loss, color = causes)) +
  geom_line() + 
  scale_y_continuous(labels = comma) +
  labs(title = "Causes of loss of forest in Brazil in 2013",
       y = "Loss (hectares)", x = "")

brazil_loss %>% 
  mutate(causes = fct_lump(causes, 6, w = loss) ) %>% 
  group_by(causes, year) %>% 
  summarize(loss = sum(loss), .groups = "drop") %>% 
  mutate(causes = fct_reorder(causes, loss)) %>% 
  ggplot(aes(year, loss, fill = causes)) +
  geom_area() + 
  scale_y_continuous(labels = comma) +
  labs(title = "Causes of loss of forest in Brazil in 2013",
       y = "Loss (hectares)", x = "")
 
```


```{r}

soybean_use <- tt$soybean_use %>% 
  filter(str_length(code) == 3) %>% 
  rename(country = entity) %>% 
  mutate(total = human_food + animal_feed + processed) %>% 
  arrange(desc(total)) %>% 
  pivot_longer(human_food:processed,
               names_to = "use",
               values_to = "amount") %>% 
  replace_na(list(amount = 0)) %>% 
  arrange(desc(total)) %>% 
  mutate(use = str_to_sentence(str_replace_all(use, "_", " ")))

soybean_use %>% 
  filter(country %in% c("Brazil", "United States", "China", "Indonesia")) %>% 
  ggplot(aes(year, amount, fill = use)) +
  geom_area() +
  facet_wrap(~ country) +
  scale_y_continuous(labels = comma) +
  labs(x = "Year", y = "Amount of Soybeans (measured in something)", fill = "")

vegetable_oil <- tt$vegetable_oil %>% 
  rename(country = entity)

vegetable_oil %>% 
  count(crop_oil, sort = T)

vegetable_oil %>% 
  filter(!is.na(production)) %>% 
  mutate(crop_oil = fct_lump(crop_oil, 5, w = production)) %>% 
  group_by(country, crop_oil, year) %>% 
  summarize(production = sum(production)) %>% 
  filter(country %in% c("United States", "China", "India", "Indonesia")) %>% 
  ggplot(aes(year, production, fill = crop_oil)) +
  geom_area() +
  scale_y_continuous(labels = comma) +
  facet_wrap(~ country)


```


```{r}

maps::iso3166 %>% 
  head()

forest <- tt$forest

country_data <- forest %>% 
  filter(year == 2010) %>% 
  inner_join(maps::iso3166, by = c(code = "a3"))

map_data("world") %>% 
  as_tibble() %>% 
  filter(region != "Antartica") %>% 
  regex_left_join(country_data, by = c(region = "mapname")) %>% 
  ggplot(aes(long, lat, group = group, fill = net_forest_conversion)) +
  geom_polygon(color = "black", size = .05) +
  scale_fill_gradient2(low = "red", high = "green", labels = comma) +
  theme_map() +
  labs(fill = "Net forest conversion (2010)")
  

```











