---
title: "TidyTemplate"
date: 2022-09-21
output: html_document
editor_options: 
  chunk_output_type: console
---

# TidyTuesday

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
library(lubridate)
library(ggthemes)
library(gganimate)
library(tidytext)
library(widyr)
library(tidygraph)
library(ggraph)
library(tidymodels)

theme_set(theme_light())

```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2022-09-13")

tt

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

bigfoot <- tt$bigfoot %>% 
  mutate(
    season = na_if(season, "Unknown"),
    title = str_remove(title, "Report \\d+\\: "),
    year = year(date),
    season = fct_relevel(season, c("Spring", "Summer", "Fall", "Winter"))
    )

```


```{r}

bigfoot %>% 
  count(season, sort = TRUE)

bigfoot %>% 
  count(classification)

bigfoot %>% 
  filter(year >= 1950) %>% 
  ggplot(aes(year, fill = classification)) +
  geom_bar()

```


```{r}

bigfoot %>% 
  count(state, sort = TRUE)

bigfoot_filtered <- bigfoot %>% 
  filter(state != "Alaska") %>% 
  filter(longitude > -130, year >= 1950) 

bigfoot_filtered %>% 
  ggplot(aes(longitude, latitude)) +
  borders("state") +
  geom_point(size = .5) +
  theme_map() +
  coord_map() +
  labs(title = "Bigfoot sightings")

bigfoot_filtered %>% 
  filter(classification != "Class C") %>% 
  ggplot(aes(longitude, latitude, color = classification)) +
  borders("state") +
  geom_point(size = .5) +
  theme_map() +
  coord_map() +
  transition_manual(year, cumulative = TRUE) +
  labs(title = "Bigfoot sightings: { current_frame }")

```


```{r}

bigfoot_filtered %>% 
  mutate(state = fct_lump(state, 8),
         state = fct_infreq(state)) %>% 
  ggplot(aes(5 * year %/% 5)) +
  geom_bar() +
  facet_wrap(~ state, scales = "free") +
  labs(x = "Year", y = "# of Sightings (in 5-year period)")

```

```{r}

bigfoot %>% 
  filter(!is.na(season)) %>% 
  count(season)

bigfoot %>% 
  filter(!is.na(season)) %>% 
  ggplot(aes(year, fill = season)) +
  geom_bar() +
  facet_wrap(~ season)

bigfoot %>% 
  filter(!is.na(season)) %>% 
  count(season, state = fct_lump(state, 8)) %>% 
  mutate(state = fct_reorder(state, n, sum)) %>% 
  ggplot(aes(n, season)) +
  geom_col() +
  facet_wrap(~ state, scales = "free_x")

```

```{r}

bigfoot %>% 
  filter(!is.na(date)) %>% 
  count(month = month(date, label = TRUE)) %>% 
  # mutate(month = fct_reorder(month, n)) %>% 
  ggplot(aes(month, n)) +
  geom_col(fill = "darkgreen") 

```


Text Analysis:

```{r}

bigfoot_title_words <- bigfoot %>% 
  select(id = number, year, season, classification, state, 
         title, observed, location_details) %>% 
  unnest_tokens(word, title) %>% 
  filter(!is.na(word)) %>% 
  anti_join(stop_words, by = "word")

bigfoot_title_words %>% 
  count(year, word = fct_lump(word, 16)) %>% 
  filter(word != "Other") %>% 
  ggplot(aes(year, n)) +
  geom_col() +
  facet_wrap(~ word, scales = "free_y")

bigfoot_title_words %>% 
  filter(year >= 1950) %>% 
  group_by(decade = 10 * year %/% 10) %>% 
  mutate(decade_total = n_distinct(word)) %>% 
  count(decade, decade_total, word = fct_lump(word, 16)) %>% 
  filter(word != "Other") %>% 
  ggplot(aes(decade, n / decade_total)) +
  geom_line() +
  expand_limits(y = 0) +
  facet_wrap(~ word, scales = "free_y") +
  scale_y_continuous(labels = percent_format()) +
  labs(x = "Decade", y = "% of titles containing this word")

bigfoot_title_words %>% 
  filter(year >= 1950) %>% 
  group_by(word) %>% 
  summarize(n = n(), 
            avg_year = mean(year)) %>% 
  filter(n >= 200) %>% 
  arrange(desc(avg_year))

```


```{r}

bigfoot_title_words %>% 
  filter(fct_lump(word, 20) != "Other") %>% 
  pairwise_cor(word, id, sort = TRUE)

bigfoot %>% 
  filter(str_detect(title, "memory")) %>% 
  pull(title)

```


```{r}

bigfoot_observed_words <- bigfoot %>% 
  select(id = number, year, season, classification, state, 
         title, observed, location_details) %>% 
  unnest_tokens(word, observed) %>% 
  filter(!is.na(word)) %>% 
  anti_join(stop_words, by = "word")

word_counts <- bigfoot_observed_words %>% 
  count(word, sort=  TRUE)

bigfoot_observed_words %>% 
  filter(fct_lump(word, 30) != "Other") %>% 
  pairwise_cor(word, id, sort = TRUE) %>% 
  head(50) %>% 
  tidygraph::tbl_graph(nodes = word_counts, edges = .) %>% 
  ggraph() +
  geom_edge_link() +
  geom_node_point()

```

### Machine Learning

Can I predict the Class (A vs. B) based on features of the data like time, weather, and text?

```{r}

set.seed(2022)
bigfoot_spl <- bigfoot %>% 
  filter(classification != "Class C") %>% 
  initial_split()

bigfoot_train <- training(bigfoot_spl)
bigfoot_test <- testing(bigfoot_spl)

bigfoot_train_fold5 <- bigfoot_train %>% 
  vfold_cv(5)

tune <- recipe(classification ~ season + year + state, 
       bigfoot_train) %>% 
  step_impute_mean(all_numeric_predictors()) %>% 
  step_ns(year, deg_free = tune()) %>% 
  step_other(all_nominal_predictors(), threshold = tune()) %>%
  workflow(logistic_reg()) %>% 
  tune_grid(bigfoot_train_fold5, 
            metrics = metric_set(roc_auc),
            grid = crossing(deg_free = seq(1, 7, 2),
                            threshold = c(.01, .1))) 

autoplot(tune)

# Linear model
lin_wf <- recipe(classification ~ season + year + state + temperature_mid + humidity + latitude + longitude, 
       bigfoot_train) %>% 
  step_impute_mean(all_numeric_predictors()) %>% 
  step_ns(year, deg_free = 6) %>% 
  step_other(all_nominal_predictors(), threshold = .01) %>%
  workflow(logistic_reg()) 

lin_wf %>% 
  fit_resamples(bigfoot_train_fold5, 
            metrics = metric_set(roc_auc)) %>% 
  collect_metrics()



```



















